---
title: "Code for Publication"
output: html_document
date: "2024-10-15"
---

```{r setup, include=FALSE,message=FALSE}
library(tidyverse)
library(plotrix)
library(viridis)
library(ggh4x) #For making leveled facets
library(ggplot2); theme_set(theme_classic())
library(patchwork)
library(cowplot)
knitr::opts_chunk$set(echo = TRUE)
```

# Main Text

## Figure 3

### Figure 3A

#### 1) Load and wrangle the data

```{r, message=FALSE}
df=read.csv("Model for Pub Fig 3A-table.csv", skip=6) |> 
  # Rename columns from BehaviorSpace output
  rename(
         Olfaction=Olfaction.Threshold, 
         #olfaction threshold. 40 for Low Olfaction, 1 for High Olfaction (odor concentration needed for detection)
         Cuing=communicate,
         #whether or not the birds were using local enhancement (actively cuing one another when they found a plume)
         Flocking=weight.flock.crosswind, 
         #whether or not the birds were using flock foraging. 0 for no, 0.95 for yes (the weight given to the flocking algorithm)
         Vision=Detection.Distance, 
         #how far away they could detect another bird 
         FoundFoodAll=X.count.turtles.with..did.find.food...1.., 
         #the number of birds that found the food source
         Birds=N.Birds 
         #The number of birds in the model (here should be 50 for all runs)
         ) |> 
  #Calculate the mean and margin of error for the success (as number of birds, not a percentage)
  group_by(Olfaction,Cuing,Flocking,Vision,Birds) |> #group by the relevant parameters to calculate the mean across all runs within each parameter space
  summarise(n=n(),
            t.score=qt(0.05/2,n-1,lower.tail = F), #calculating a t-score for the margin of error (95%)
            Success.se=std.error(FoundFoodAll,na.rm=T),#calculating the standard error for the margin of error
            margin.of.error=t.score*Success.se, #calculating the margin of error
            Success=mean(FoundFoodAll,na.rm=T), #the mean success rate 
            ) %>% 
  ungroup() |> 
  #Create a column that is the "strategy" being used (the \n allows for tidier legends in the plots)
  ##Network Foraging if there is flock foraging (i.e. flocking ==0.95) and local enhancement (i.e. cuing==true). 
  ##Flock foraging when flocking==0.95 but cuing==false
  ##Local Enhancement when flocking==0 but cuing ==true
  ##Olfaction Only when flocking==0 and cuing==false
  mutate(Strategy=if_else(Flocking==0 & Cuing=="false", "Olfaction \nOnly",
                          if_else(Flocking==0 & Cuing=="true","Local \nEnhancement",
                                  if_else(Flocking==0.95 & Cuing == "false", "Flock \nForaging", "Network \nForaging")))) |> 
  mutate(Strategy=factor(Strategy,levels=c("Network \nForaging","Local \nEnhancement","Flock \nForaging", "Olfaction \nOnly"))) |> 
  #Turn Olfactory Sensitivity into a factor
  mutate(Olfaction=if_else(Olfaction==1,"High Olfaction","Low Olfaction")) |> 
  #Calculate the Success Rate and margin of error as a percentage of the total group size (must be done in this order)
  mutate(Success=(Success/Birds)*100,
         margin.of.error=(margin.of.error/Birds)*100) |> 
  #Select columns of interest
  dplyr::select(Olfaction,Strategy,Vision,Birds,Success,margin.of.error)
```

#### 2) Make plot 3A and perform other calculations included in text

```{r,fig.width=10, fig.height=5}
(p1=df |> 
    ggplot(aes(x=Vision,y=Success,fill=Strategy,color=Strategy, group=Strategy,linetype=Strategy))+
     theme_classic()+
     theme(text = element_text(size=20),
           legend.key.width = unit(4,"line"),
           legend.key.spacing.y = unit(0.4, "cm"),
           plot.margin = margin(0, 0, 0, 0, "pt")
           )+
     ylab("Success (%)")+
     xlab("Visual Detection Range (Body-Lengths)")+
     scale_y_continuous(limits = c(0,100))+
      scale_color_viridis(discrete = TRUE,option="viridis")+
      scale_fill_viridis(discrete = TRUE,option="viridis")+
      scale_linetype_manual(values=c("11","23","73","solid"))+
      geom_ribbon(aes(ymin=Success-margin.of.error, ymax=Success+margin.of.error), alpha=0.3, color=NA)+
      geom_line(aes(),linewidth=1.8)+
      theme(panel.spacing = unit(1, "lines"))+
      facet_grid(~Olfaction) 
)

#Success rates for Olfaction Only Strategy for High and Low Olfaction
df |> 
  filter(Strategy=="Olfaction \nOnly") |> 
  distinct(Olfaction,Success,margin.of.error) |> 
  reframe(
    "Olfaction"=Olfaction,
    "Success and Error"=paste0(round(Success,digits=1)," ± ",round(margin.of.error,digits = 1))
    )
#Highest Success Rate
df |> 
  filter(Success>=90) |> 
  reframe(
    "Strategy"=Strategy,
    "Vision"=Vision,
    "Olfaction"=Olfaction,
    "Success and Error"=paste0(round(Success,digits=1)," ± ",round(margin.of.error,digits = 1))
    )

#Success Rates for other strategies by Olfaction and Vision
df |> 
  filter(Strategy!="Olfaction \nOnly", Vision==10 | Vision==50) |> 
  dplyr::select(Strategy,Vision,Olfaction,Success) |> 
  group_by(Olfaction,Strategy) |> 
  #for each strategy/olfaction, the success rate when Vision=50, the success rate when Vision=10, and the difference between these
  summarise(S10=round(Success[Vision==10],digits=1),S50=round(Success[Vision==50],digits=1),SDiff=S50-S10)
```

### Figure 3B

#### 1) Load and wrangle the data

```{r, message=FALSE}
#several models were run with different population sizes, though not all were used for figure simplicity
df2=rbind(read.csv("Model for Pub Fig 3B Pop 10-table.csv", skip=6),read.csv("Model for Pub Fig 3B Pop 20 30 40-table.csv",skip=6)
          ) |> 
  # Rename columns as above
  rename(
         Olfaction=Olfaction.Threshold,
         Cuing=communicate,
         Flocking=weight.flock.crosswind,
         Vision=Detection.Distance,
         FoundFoodAll=X.count.turtles.with..did.find.food...1..,
         Birds=N.Birds
         ) |> 
  #Calculate the mean and margin of error for the success (as number of birds) as above
  group_by(Olfaction,Cuing,Flocking,Vision,Birds) %>% 
  summarise(n=n(),
            t.score=qt(0.05/2,n-1,lower.tail = F),
            Success.se=std.error(FoundFoodAll,na.rm=T),
            margin.of.error=t.score*Success.se,
            Success=mean(FoundFoodAll,na.rm=T),
            ) %>% 
  ungroup() |> 
  #Create a column that is the "strategy" being used (the \n allows for tidier legends) as above
  mutate(Strategy=if_else(Flocking==0 & Cuing=="false", "Olfaction \nOnly",
                          if_else(Flocking==0 & Cuing=="true","Local \nEnhancement",
                                  if_else(Flocking==0.95 & Cuing == "false", "Flock \nForaging", "Network \nForaging")))) |> 
  mutate(Strategy=factor(Strategy,levels=c("Network \nForaging","Local \nEnhancement","Flock \nForaging", "Olfaction \nOnly"))) |> 
  #Turn Olfactory Sensitivity into a factor as above
  mutate(Olfaction=if_else(Olfaction==1,"High Olfaction","Low Olfaction")) |> 
  #Calculate the Success Rate and margin of error as a percentage of the total group size (must be done in this order)
    mutate(Success=(Success/Birds)*100,
           margin.of.error=(margin.of.error/Birds)*100) |> 
  #Select columns of interest
  dplyr::select(Olfaction,Strategy,Vision,Birds,Success,margin.of.error) |> 
  #The df loaded in the previous section is the version of the model with population =50, so we bind it here. Not actually used for the plot but used for calculations
  rbind(df)
```

#### 2) Make plot 3B and perform other calculations included in text

```{r,fig.width=12, fig.height=4, message=FALSE}
(p2=df2 |> 
   filter(Birds!=50,Birds!=30) |> 
   mutate(Birds=as.factor(paste0("Pop:",Birds))) |> 
   mutate(Birds=factor(Birds,levels = c( "Pop:40","Pop:20", "Pop:10"))) |>   
   ggplot(aes(x=Vision,y=Success,fill=Strategy,color=Strategy, group=Strategy,linetype=Strategy))+
     theme_classic()+
     theme(text = element_text(size=20),
           legend.key.width = unit(4,"line"),
           legend.key.spacing.y = unit(0.4, "cm"),
           axis.text.x = element_text(size=15),
           plot.margin = margin(0, 0, 0, 0, "pt")
           )+
      ylab("Success (%)")+
      xlab("Visual Detection Range (Body-Lengths)")+
      scale_y_continuous(limits = c(0,100))+
      scale_color_viridis(discrete = TRUE,option="viridis")+
      scale_fill_viridis(discrete = TRUE,option="viridis")+
      scale_linetype_manual(values=c("11","23","73","solid"))+
      geom_ribbon(aes(ymin=Success-margin.of.error, ymax=Success+margin.of.error), alpha=0.3, color=NA)+
      geom_line(aes(),linewidth=1.8)+
      theme(panel.spacing.x = unit(c(0.1,0.1,1,0.1,0.1), "lines"))+
      facet_nested(~Olfaction+Birds) +
      scale_x_continuous(limits = c(10,55),breaks = c(15,30,45))
)


#comparing the success rates for pop=50 to pop=10, for each detection range, social strategy and olfaction threshold 

df2 |> 
  filter(Strategy!="Olfaction \nOnly") |> 
  dplyr::select(Olfaction,Birds,Vision,Success,Strategy) |> 
  group_by(Olfaction,Strategy,Vision) |> 
  #for each strategy/olfaction, the success rate when pop=50, the success rate when pop=10, and the difference between these
  summarize(S50=Success[Birds==50],S10=Success[Birds==10], successdiff=round(S50-S10,digits=1)) |> 
  select(Olfaction,Strategy,Vision,successdiff) |> 
  #run from 50 to 10
  arrange(desc(Vision)) |> 
  #pivot to show the difference in success rates from pop=50 to pop=10 for each detection range
  mutate(Vision=paste0("Diff_S for Vision=",Vision)) |> 
  pivot_wider(names_from = Vision,values_from = successdiff)
```

### Figure 3 \-- Combined

```{r, warning=FALSE,results="hide"}
# get just the legend
legend_grob=cowplot::get_legend(p1)
#remove legend from other plots
p1.2=p1+theme(legend.position = "none")
p2.1=p2+theme(legend.position = "none")

#build a theme to get the plot levels (A and B) to have the formatting we want (bold and size 16) even though they are technically title elements
thm <- theme(plot.title = element_text(face = 2, size = 16))
#build bottom plot with tag=B, and top plot that combines the legend and has tag=A
bottom.plot=wrap_elements((p2.1) + plot_annotation(title = "B", theme=thm))
top.plot=wrap_elements((p1.2|legend_grob) + plot_annotation(title = "A", theme=thm))
```

```{r,fig.width=11, fig.height=8}
top.plot/bottom.plot 

#ggsave("../Figure 3.png")
```

## Figure 4

### 1) Load and wrangle the data

```{r, message=FALSE}
# The model where ALL 50 birds have high olf and vision = 10 comes from the first data table, loaded in section Figure 3A, from runs where Olfaction="Low Olfaction" and Vision = 10. Select only those runs here and add a column to indicate the number of birds with NO OLFACTION AT ALL (NumNoOlf) is 0 out of 50
df.AllNoOlf =df |> 
  filter(Olfaction=="High Olfaction",Vision==10) |> 
  #remove columns not being used
  dplyr::select(-Vision,-Olfaction,-Birds) |> 
  #Add column "NumNoOlf" which is the number of birds with NO olfaction at all (for this model, 0 out of all 50 birds)
  mutate(NumNoOlf=0)
  
#Several models were run to get the full range of proportions of species. Here we load and bind them together
df3=rbind(
  #NumNoOlf= 5, 10, 20, 40 (Seed=1:500)
  read.csv("Model for Pub Fig 4_NumNoOlf_5 to 40-table.csv", skip=6),
  
  #NumNoOlf= 50 (Seed=1:500)
  read.csv("Model for Pub Fig 4_NumNoOlf_50-table.csv", skip=6),
  
  #NumNoOlf= 42, 44, 46, 48 (Seed=1:100)
  read.csv("Model for Pub Fig 4_NumNoOlf_42 to 48 Seed 1 to 100-table.csv", skip = 6),
  
  #NumNoOlf= 30, 49 (Seed=1:100)
  read.csv("Model for Pub Fig 4_NumNoOlf_30 and 49 Seed 1 to 100-table.csv", skip=6),
  
  #NumNoOlf= 30, 42, 44, 46, 48, 49 (Repeated for Seed=101:500)
  read.csv("Model for Pub Fig 4_NumNoOlf_30 to 49 Seed 101 to 500-table.csv", skip = 6),
  
  #NumNoOlf= 25 (Seed=1:100)
  read.csv("Model for Pub Fig 4_NumNoOlf_25-table.csv", skip=6),
  
  #NumNoOlf= 15, 35 (Seed=1:100)
  read.csv("Model for Pub Fig 4_NumNoOlf_15 and 35-table.csv", skip=6)
  )|> 
 # Rename columns as above plus NumNoOlf
  rename(
         Cuing=communicate,
         Flocking=weight.flock.crosswind,
         FoundFoodAll=X.count.turtles.with..did.find.food...1..,
         #This column was named particularly poorly. It represents the number of Birds with NO olfaction (Olfaction threshold for detection > max odor) but high vision (vision = 50). It was originally called Number.Of.Low.Olf in the code, but should more properly be the Number of NO Olf, and has been renamed accordingly
         NumNoOlf=Number.Of.Low.Olf 
         ) |> 
  #Calculate the mean and margin of error for the success (as number of birds) as above
  group_by(Cuing,Flocking,NumNoOlf) %>% 
  summarise(n=n(),
            t.score=qt(0.05/2,n-1,lower.tail = F),
            Success.se=std.error(FoundFoodAll,na.rm=T),
            margin.of.error=t.score*Success.se,
            Success=mean(FoundFoodAll,na.rm=T),
            ) %>% 
  ungroup() |> 
  #Create a column that is the "strategy" being used (the \n allows for tidier legends) as above
  mutate(Strategy=if_else(Flocking==0 & Cuing=="false", "Olfaction \nOnly",
                          if_else(Flocking==0 & Cuing=="true","Local \nEnhancement",
                                  if_else(Flocking==0.95 & Cuing == "false", "Flock \nForaging", "Network \nForaging")))) |> 
  mutate(Strategy=factor(Strategy,levels=c("Network \nForaging","Local \nEnhancement","Flock \nForaging", "Olfaction \nOnly"))) |> 
  #Calculate the Success Rate and margin of error as a percentage of the total group size (must be done in this order) as above
  mutate(Success=(Success/50)*100,
         margin.of.error=(margin.of.error/50)*100) |> 
  #Select columns of interest
  dplyr::select(Strategy,Success,margin.of.error,NumNoOlf) |> 
  #Bind to the above df with NumNoOlf=0
  rbind(df.AllNoOlf)  
```

### 2) Make plot 4 and perform other calculations included in text

```{r, fig.width=10, fig.height=5}
(p3=df3 |> 
  ggplot(aes(x=NumNoOlf,y=Success,fill=Strategy,color=Strategy, group=Strategy,linetype=Strategy))+
      theme(text = element_text(size=20),
            legend.key.width = unit(4,"line"),
            legend.key.spacing.y = unit(0.4, "cm")
           )+
      ylab("Success (%)")+
      scale_y_continuous(limits = c(0,100))+
      scale_color_viridis(discrete = TRUE,option="viridis")+
      scale_fill_viridis(discrete = TRUE,option="viridis")+
      scale_linetype_manual(values=c("11","23","73","solid"))+
      geom_ribbon(aes(ymin=Success-margin.of.error, ymax=Success+margin.of.error), alpha=0.3, color=NA)+
      geom_line(aes(),linewidth=1.8)+
      theme(panel.spacing = unit(1, "lines"))+
      scale_x_continuous(labels=~paste(50-.,.,sep=" | "),
                      name="Number of birds in each species")
   
   )
#ggsave("../Figure 4.png")

#Success Rate for Olfaction Only for each group proportion
filter(df3, Strategy=="Olfaction \nOnly") |> 
  group_by(NumNoOlf) |> 
  reframe("Success and Error"=paste0(round(Success)," ± ",round(margin.of.error)))

#Success Rate for Flock Foraging when compared to the max Olfaction Only Success Rate (NumNoOlf=0, i.e. Success Rate = 47)
filter(df3,Strategy=="Flock \nForaging") |> 
  group_by(NumNoOlf) |> 
  reframe("Success and Error"=paste0(round(Success)," ± ",round(margin.of.error)),
          "Success Comp OlfOnly"=round(Success-47)) |> 
  mutate(PercentNoOlf=(NumNoOlf/50)*100)

#Success Rate for Network Foraging when compared to the max Olfaction Only Success Rate (NumNoOlf=0, i.e. Success Rate = 47)
filter(df3,Strategy=="Network \nForaging") |> 
  group_by(NumNoOlf) |> 
  reframe("Success and Error"=paste0(round(Success)," ± ",round(margin.of.error)),
          "Success Comp OlfOnly"=round(Success-47))|> 
  mutate(PercentNoOlf=(NumNoOlf/50)*100)

#Success Rate for Local Enhancement when compared to the max Olfaction Only Success Rate (NumNoOlf=0, i.e. Success Rate = 47)
filter(df3,Strategy=="Local \nEnhancement") |> 
  group_by(NumNoOlf) |> 
  reframe("Success and Error"=paste0(round(Success)," ± ",round(margin.of.error)),
          "Success Comp OlfOnly"=round(Success-47))|> 
  mutate(PercentNoOlf=(NumNoOlf/50)*100)
```

# Supplemental Information

## Figure S1

```{r, fig.width=10, fig.height=5, message=FALSE}
library(readxl)

eye.df=read_excel("eye diameter versus cube root of mass for birds.xls")|> 
  rename(Eye=`eye diameter (mm)`,MassCubeRoot=`cube root of mass`) |> 
  mutate(Order=if_else(order=="Procellariiformes","Procellariiformes","Other"))


#Only Procellariiformes
Procellariiformes=filter(eye.df, Order!="Other")

ggplot()+
  geom_point(data=eye.df,aes(log(MassCubeRoot),log(Eye), color=Order),size=1.5, alpha=0.5)+
  geom_smooth(data=eye.df,aes(log(MassCubeRoot),log(Eye), color=Order),method = "lm")+
  
  geom_point(data=Procellariiformes,aes(log(MassCubeRoot),log(Eye)),color="red",size=3)+
  geom_smooth(data=Procellariiformes,aes(log(MassCubeRoot),log(Eye)), color="red",method = "lm")+
  
  scale_color_manual(values=c("black","red"))+
  theme(text = element_text(size=18))+
      ylab("Log10 ( Eye Diameter in mm )")+
      xlab("Log10 ( Cube Root of Mass in grams )")
#ggsave("../Figure S1.png")
```

## The Odor Plume: Figure S2 and corresponding calculations

This is data from a BehaviorSpace model where we reloaded the world from seeds 1:100 and output a list of all patches' intensity. Note: The data may take some time to load.

```{r, fig.width=5, fig.height=3,message=FALSE}
# Load the data
Intensity = read.csv("Model for Parameterization Intensity Ranges-table.csv", skip = 6) |> 
  dplyr::select(run=X.run.number.,Intensity=list..intensity..of.patches) |> #select the relevant columns
  mutate(Intensity=gsub('\\[','',Intensity), #remove the square brackets in the intensity column
         Intensity=gsub('\\]','',Intensity)) |> 
  separate_wider_delim(Intensity,delim=" ",names_sep="") |> #split the intensity column by spaces
  pivot_longer(!run) |> #pivot longer
  dplyr::select(-name) |> #remove the name column
  mutate(value=as.numeric(value)) |> #set the intensity column to be numeric
  filter(value>0) #get rid of patches that weren't a part of the odor plume

# Plot/analyze the data

#Figure S2
Intensity |> 
  ggplot()+ 
  geom_histogram(aes(value, group=as.factor(run)), bins=50, position = "identity", alpha=0.3)+
  theme(legend.position = "none")+
  xlab("Odor Intensity")
#ggsave("../Figure S2.png")

#mean over all 100 runs
round(mean(Intensity$value))

#across all 100 runs, what was the smallest, largest, and mean of the maximum odorant value
Intensity |> 
  group_by(run) |> 
  #max value for each run
  summarise(maxvalue=max(value)) |> 
  ungroup() |> 
  #across all of those, the min, max, and mean of this max value
  summarise(minmax=round(min(maxvalue)), maxmax=round(max(maxvalue)), meanmax=round(mean(maxvalue)))

#Get the average total area covered by the plume, as well as the average area of the plume that is >=40 (as a percentage of the total)
Intensity |> 
  mutate(Over40=if_else(value>=40,"Over40","Under40")) |> #create a column to designate if the value is over 40
  group_by(run, Over40) |> 
  summarise(n=n()) |> #count the number of patches over and under 40 for each run
  pivot_wider(names_from = Over40, values_from = n) |> #pivot to columns
  mutate(All=Over40+Under40) |> #create a column that is the sum of over and under (total area covered by the plume)
  mutate(Percentage40=(Over40/All)*100) |> #percentage of the total that is over 40
  ungroup() |> 
  summarise(mean(All), mean(Over40),mean(Percentage40)) #find the average across all runs
```

## Parameterizing the Olfactory Search Algorithm: Figure S3 and corresponding calculations

There are four variables within the olfactory search algorithm to parameterize: - The turning angle during the zigzags, i.e. how large of an offset from upwind do they turn (hereafter "Angle ZigZag")) - How long they continue moving upwind after losing the scent, i.e. do they immediately zigzag or keep going upwind for a bit. ("Time Upwind") - For each zigzag, how long do they maintain that particular heading, i.e. how far do they go for each leg of the zig vs zag ("Each ZigZag") - How long in total do they spend performing the upwind+zigzag behavior before returning to flock/crosswind? ("Total Time ZigZag")

We ran a behavior space model for agents using the olfactory search algorithm ONLY (flock=no, cueing=no) for agents with high (1) and low (40) olfaction thresholds.

We iterated over: - Angle: 10, 20, 45, 70, 90 deg - Total: 10, 20, 40, 60, 80 ticks - Upwind and Each ZigZag: 5, 10, 15 ticks

This was repeated from seed 1:100

```{r,message=FALSE,fig.width=10, fig.height=5}
#Load the Data for all seeds
olfAlgSeed=read.csv("Model for Parameterization Parameterize Olf Algorithm Time and Angles-table.csv", skip=6)|> 
  dplyr::select(Seed,Angle=ZigZagAngle,ZigZag=TimeZigZagging,Upwind=TimeUpWind,Total=TotalTimeSpentZigZagging,Success=X..count.turtles.with..did.find.food...1.....N.Birds....100, Olfaction=Olfaction.Threshold) |> 
   mutate(Olf=if_else(Olfaction==1,"High","Low"))
#success rates averaged across seeds
olfAlg=olfAlgSeed |> 
  group_by(Olf, Angle, Total, Upwind,ZigZag) |>
   summarise(Success=mean(Success))

#Analyze the Data

#Within a seed, how much does varying the variable of interest change the success rate for each variable
##function to give you the difference in the success rate from the min to max value for each variable with all other values held constant
ImpactOfVar=function(Variable){
  tmp=olfAlgSeed |> 
    rename(Variable=!!Variable) |> 
    group_by_at(vars(c(-Success,-Variable))) |> 
    summarise(deltaSuccess=max(Success)-min(Success)) |> 
    ungroup() |> summarise(delta=mean(deltaSuccess))
    
  tmp$delta
}
##apply to each variable and then pivot to see which variables had the biggest impact on success
data.frame(ZigZag=ImpactOfVar("ZigZag"),Upwind=ImpactOfVar("Upwind"),Total=ImpactOfVar("Total"),Angle=ImpactOfVar("Angle"))|> 
  pivot_longer(cols = everything(), names_to = "variable", values_to = "Change in Success")


#Figure S3: All variables: Success vs Total, colored by Angle, faceted by Upwind and ZigZag, additionally nested by Olfaction. Averages for each seed.
olfAlg |> 
  mutate("Angle ZigZag"=as.factor(Angle) ) |> 
  rename("Olfaction"=Olf, "Time ZigZag (ticks)"=Total, "Each ZigZag"=ZigZag,"Time Upwind"=Upwind,"Success (%)" =Success)|> 
  ggplot(aes(`Time ZigZag (ticks)`,`Success (%)`,color=`Angle ZigZag`, group=`Angle ZigZag`))+
  geom_path( linewidth=2, alpha=0.5)+
  geom_point()+
  facet_nested(`Each ZigZag`~`Olfaction`+`Time Upwind`, labeller = label_both)+
  scale_color_viridis(discrete = T)
#ggsave("../Figure S3.png")

#A few more plots not included in the supp but that show these effects in better detail

#Success vs upwind, colored by each zigzag (facted by olf). This shows there is almost no effect of ZigZag, and that success was slightly higher at larger Time Upwind 
olfAlg |> 
  group_by(Upwind,ZigZag,Olf) |> 
  summarise(Success=mean(Success)) |> 
  ggplot(aes(Upwind,Success,color=ZigZag, group=ZigZag))+
  geom_path( linewidth=2, alpha=0.5)+
  geom_point()+
  scale_color_viridis()+
  facet_wrap(~Olf, labeller = label_both)

#Success vs Total, colored by Angle. This shows that angle was relatively flat up until 45 degrees
olfAlg |> 
  group_by(Angle,Total,Olf) |> 
  summarise(Success=mean(Success)) |> 
  mutate("Angle ZigZag"=as.factor(Angle) ) |> 
  ggplot(aes(Total,Success,color=`Angle ZigZag`, group=`Angle ZigZag`))+
  geom_path( linewidth=2, alpha=0.5)+
  geom_point()+
  scale_color_viridis(discrete = T)+
  facet_wrap(~Olf, labeller = label_both)

#Just Total time zigzag with new values for other parameters showing the different relationship for different Olfactions
olfAlg |> 
  filter(Angle==45, ZigZag==5,Upwind==15) |> 
  ggplot(aes(Total,Success, color=as.factor(Olf)))+
  geom_point(linewidth=5)+
     geom_line()
```

## Parameterizing the Flocking Algorithm: Figure S4

There are two variables to parameterize within the flocking algorithm: - the max turning angle for Cohere/Align - the max turning angle for Separate.

We ran a behavior space model for agents using the Flock Foraging algorithm ONLY (flock=yes, cue=no) for agents with high (1) and low (40) olfaction. For all models, ZigZag Angle=45, Time Upwind=15, Each ZigZag=5, and Time ZigZag=60. Additionally, we set the minimum separation = 6, and the detection range = 50 (other preliminary data indicated this was an optimal combination).

We iterated over: - max-separate-turn: 0.5, 1, 1.5, 2 deg - max-align-cohere-turn: 1, 10, 20, 40 deg (Note: from general observations of the model, whenever max-sepatate-turn is \> 2 deg, the behavior of the agents no longer looks like flocking behavior (jerky and unrealistic), and the same occurs for max-align-cohere-turn above 40 deg.)

This was repeated from seed 1:50

```{r, fig.width=7, fig.height=3, message=FALSE}

read.csv("Model for Parameterization Parameterize max turn angle-table.csv", skip=6) |> 
  dplyr::select(Olfaction=Olfaction.Threshold,Seed,SepTurn=max.separate.turn, AlignCohereTurn=max.align.cohere.turn, Success=X..count.turtles.with..did.find.food...1.....N.Birds....100) |> 
  group_by(Olfaction, SepTurn, AlignCohereTurn) |> 
  summarise(Success=mean(Success)) |> 
  ungroup() |> 
  mutate(Olfaction=if_else(Olfaction==1,"High Olfaction","Low Olfaction")) |> 
  mutate(AlignCohereTurn=as.factor(AlignCohereTurn)) |> 
    ggplot(aes(SepTurn, Success,color=AlignCohereTurn, group=AlignCohereTurn))+
    geom_point(size=3,stroke=1)+
    geom_line(linewidth=1.2)+
    theme(panel.spacing = unit(1, "lines"))+
    scale_color_viridis(discrete = T)+
    facet_wrap(~Olfaction)+
    scale_y_continuous(limits = c(0,95))
#ggsave("../Figure S4.png")
```

## Parameterizing the relationship between Separation and Detection Range: Figure S5

We ran a behaviorspace model for agents using the Flock Foraging and Network Foraging algorithms (flock=yes, cue=yes & no) for agents with high (1) and low (40) olfaction. For all models, ZigZag Angle=45, Time Upwind=15, Each ZigZag=5, Time ZigZag=60, max-separate-turn=2, and max-align-cohere-turn=40.

We iterated over: - Vision (or detection range): 10, 20, 30, 40 50 patches - Sep (minimum separation): 1, 2, 3, 4, 5, 6, 7 patches

This was repeated from seed 1:100 for all variable space.

```{r, fig.width=10, fig.height=5, message=FALSE}
VisionSep=read.csv("Model for Parameterization Parameterize Vision and Separation-table.csv", skip=6)|> 
  dplyr::select(Flocking=weight.flock.crosswind,Cuing=communicate,Olfaction=Olfaction.Threshold,Seed,Sep=minimum.separation,Vision=Detection.Distance,SepTurn=max.separate.turn,Success=X..count.turtles.with..did.find.food...1.....N.Birds....100) |> 
  group_by(Cuing, Olfaction,Sep, Vision) |> 
  summarise(Success=mean(Success)) |> 
  ungroup() |> 
  mutate(Strategy=if_else(Cuing == "false", "Flock Foraging", "Network Foraging")) |> 
  mutate(Strategy=factor(Strategy,levels=c("Network Foraging","Flock Foraging"))) |> 
  mutate(Olfaction=if_else(Olfaction==1,"High","Low"))
  

#Fig S5
VisionSep |> 
   ggplot(aes(x=Sep,y=Success,fill=Vision,color=Vision, group=Vision))+
    theme(text = element_text(size=20))+
    ylab("Success (%)")+
    scale_y_continuous(limits = c(0,100))+
    scale_color_viridis()+
    scale_fill_viridis()+
    geom_line(linewidth=1.2,alpha=0.5)+
    geom_point(size=3,alpha=0.5)+
    theme(panel.spacing = unit(1, "lines"))+
    facet_nested(~Strategy+Olfaction, labeller = label_both)+
    labs(color="Detection \nRange", fill="Detection \nRange")
#ggsave("../Figure S5.png")

#what Sep yields the highest success rate for each Detection Range? (excluding Flock Foraging with Low Olf)
VisionSep |> 
   filter(Strategy!="Flock Foraging" | Olfaction !="Low") |> 
  dplyr::select(Strategy,Olfaction,Sep, Vision, Success) |> 
  group_by(Strategy,Olfaction,Vision) |> 
  filter(Success==max(Success)) |> 
  arrange(Vision,Strategy, Olfaction) |> 
  group_by(Vision) |> 
  summarize(mean(Sep)) |> 
  mutate(SepBasedOnFormula=(Vision/10)+1)
```

## Figure S6

```{r, message=FALSE}
#reload the same dataframe as for figure 3A
df.OdorOnly=read.csv("Model for Pub Fig 3A-table.csv", skip=6) |> 
  rename(
         Olfaction=Olfaction.Threshold,
         Cuing=communicate,
         Flocking=weight.flock.crosswind,
         Vision=Detection.Distance,
         FoundOdorOnly=X.count.turtles.with..ever.find.odor...1.and.did.find.food...0.. #Birds that found the odor but did not find the food
         ) |> 
  group_by(Olfaction,Cuing,Flocking,Vision) %>% 
  summarise(
            n=n(),
            t.score=qt(0.05/2,n-1,lower.tail = F),
            #Birds that found the odor but did not find the food
            OdorOnly.se=std.error(FoundOdorOnly,na.rm=T),
            MOE.OdorOnly=t.score*OdorOnly.se,
            Success.OdorOnly=mean(FoundOdorOnly),
             ) |> 
    
  ungroup() |> 
  mutate(Strategy=if_else(Flocking==0 & Cuing=="false", "Olfaction \nOnly",
                          if_else(Flocking==0 & Cuing=="true","Local \nEnhancement",
                                  if_else(Flocking==0.95 & Cuing == "false", "Flock \nForaging", "Network \nForaging")))) |> 
  mutate(Strategy=factor(Strategy,levels=c("Network \nForaging","Local \nEnhancement","Flock \nForaging", "Olfaction \nOnly"))) |> 
   mutate(Olfaction=if_else(Olfaction==1,"High Olfaction","Low Olfaction")) |> 
  
  
   mutate(Success.OdorOnly=(Success.OdorOnly/50)*100,
          MOE.OdorOnly=(MOE.OdorOnly/50)*100,
          ) |> 
  dplyr::select(Olfaction,Strategy,Vision,Success.OdorOnly,MOE.OdorOnly) 
```

Chances of finding the odor but NOT finding the food should decrease

```{r,fig.width=12, fig.height=6}
(df.OdorOnly |> 
    ggplot(aes(x=Vision,y=Success.OdorOnly,fill=Strategy,color=Strategy, group=Strategy,linetype=Strategy))+
      theme_classic()+
      theme(text = element_text(size=24),
           legend.key.width = unit(4,"line"),
           legend.key.spacing.y = unit(0.4, "cm")
           )+
      ylab("Found Odor But Not Food (%)")+
      xlab("Detection Range (Body-Lengths)")+
      scale_y_continuous(limits = c(0,25))+
      scale_color_viridis(discrete = TRUE,option="viridis")+
      scale_fill_viridis(discrete = TRUE,option="viridis")+
      scale_linetype_manual(values=c("11","23","73","solid"))+
      geom_ribbon(aes(ymin=Success.OdorOnly-MOE.OdorOnly, ymax=Success.OdorOnly+MOE.OdorOnly), alpha=0.3, color=NA)+
      geom_line(aes(),linewidth=1.8)+
      theme(panel.spacing = unit(1, "lines"))+
      facet_grid(~Olfaction) 
)
#ggsave("../Figure S6.png")
```
